RTS AI: Problems and Techniques

### 2015-12-14 ECGG_RTSProblems/ECGG_RTSProblems.tex
Add cross references

>>>>

\section*{Cross References}
In the Springer Encyclopedia of Computer Graphics an Games volume 1:
\begin{itemize}
\item Umair Azfar Khan and Yoshihiro Okada, {\it Genetic Algorithm Based NPC Making}.
\item David Churchill, Mike Preuss, Florian Richoux, Gabriel Synnaeve,
  Alberto Uriarte and Santiago Ontañón, {\it StarCraft Bots and Competitions}.
\item Jacob Schrum, {\it Constructing Game Agents Through Simulated Evolution}.
\item Sehar Shahzad Farooq and Kyung-Joong Kim, {\it Game Player Modeling}.
\item Mark H.M. Winands, {\it Monte Carlo Tree Search}.
\item Kazuki Yoshizoe and Martin Mueller, {\it Computer Go}.
\end{itemize}
